Evaluating the Performance and Energy Efficiency of COSMO-ART, a Fully Online Coupled Model System with Numerical Weather Forecast and Chemical Transport Models

### 2014-04-07 paper_enahpc14/Sec3:Evaluation.tex
updates tables

\subsection{Run configuration}
\label{subsec:3.2}
The COSMO-ART model uses NAMELIST-input to specify runtime parameters
splitted into several groups:

\begin{itemize}
\item LMGRID: specifying the domain and the size of the grid,
\item RUNCTL: parameters for the model run,
\item TUNING: parameters for tuning physics and dynamics,
\item DYNCTL: parameters for the adiabatic model,
\item PHYCTL: parameters for the diabatic model,
\item COSMO\_ART: parameters for gases and aerosols model,
\item DIACTL: parameters for the diagnostic calculations,
\item SATCTL: controlling computation of synthetic satellite images,
\item IOCTL: controlling the I/O environment,
\item GRIBIN: controlling the grib input,
\item GRIBOUT: controlling the grib output,
\end{itemize}

@@

\subsubsection{Monch (CSCS - ETH Zurich)}
\begin{figure*}
  \includegraphics[width=0.4\textwidth]{Figs/NRJ_benchmark_Monch.eps}
  \caption{Isola E1 Rack 2 Total Power and Isola E1 Total Power}
  \label{fig:1}
\end{figure*}

@@

The power  consumption for  both jobs is  calculated by  averaging the
corresponding power  measurements from the Excel  file.  Power results
account for the  Isola E1 Rack 2 Total Power. As  time resolution is 5
minutes  for the  output  results, the  average  power consumption  is
computed   by  considering  6   values  for   each  single   run  (see
Table~\ref{tab:1}).

\begin{table}
  \begin{center}
    \caption{}
    \label{tab:1}
    \begin{tabular}{lll}
      \hline\noalign{\smallskip}
      Time & Measured power (W) & Average power (W)  \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      12:55:00 & 1.2355833333e+04 & 1.265852278e+04 \\ 
      13:00:00 & 1.2820266667e+04 &  \\
      13:05:00 & 1.2600743333e+04 &  \\ 
      13:10:00 & 1.2811580000e+04 &  \\
      13:15:00 & 1.2609680000e+04 &  \\
      13:20:00 & 1.2753033333e+04 &  \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      14:30:00 & 1.2019266667e+04 & 1.258640833e+04 \\ 
      14:35:00 & 1.2632253333e+04 &  \\
      14:40:00 & 1.2779040000e+04 &  \\
      14:45:00 & 1.2753180000e+04 &  \\
      14:50:00 & 1.2610476667e+04 &  \\
      14:55:00 & 1.2724233333e+04 &  \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

@@

\subsubsection{Pilatus (CSCS - ETH Zurich)}
\begin{figure*}
  \includegraphics[width=0.4\textwidth]{Figs/NRJ_benchmark_Pilatus.eps}
  \caption{Isola HD Pilatus Total Power}
  \label{fig:2}
\end{figure*}

@@

Again, the power  consumption for all jobs is  calculated by averaging
the  corresponding  power  measurements  from the  Excel  file.  Power
results  account  for  the  Isola  HD Pilatus  Total  Power.  As  time
resolution  is 5  minutes for  the output  results, the  average power
consumption is computed by considering  4 values for each single 1-day
run and 9 values for the 2-days run (see Table~\ref{tab:2}).

\begin{table}
  \begin{center}
    \caption{}
    \label{tab:2}
    \begin{tabular}{lll}
      \hline\noalign{\smallskip}
      Time & Measured power (W) & Average power (W)  \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
       13:10:00 & 1.7824080000e+04 & 1.812201417e+04 \\ 
       13:15:00 & 1.8293650000e+04 &  \\ 
       13:20:00 & 1.8125140000e+04 &  \\ 
       13:25:00 & 1.8245186667e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       13:50:00 & 1.7849206667e+04 & 1.797961083e+04 \\ 
       13:55:00 & 1.7977790000e+04 &  \\ 
       14:00:00 & 1.8030646667e+04 &  \\ 
       14:05:00 & 1.8060800000e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       14:30:00 & 1.7868826667e+04 & 1.806545167e+04 \\ 
       14:35:00 & 1.8115786667e+04 &  \\ 
       14:40:00 & 1.8188520000e+04 &  \\ 
       14:45:00 & 1.8088673333e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       15:15:00 & 1.7857800000e+04 & 1.797302833e+04 \\ 
       15:20:00 & 1.7962513333e+04 &  \\ 
       15:25:00 & 1.8078226667e+04 &  \\ 
       15:30:00 & 1.7993573333e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       15:45:00 & 1.7801980000e+04 & 1.799757815e+04 \\ 
       15:50:00 & 1.7925386667e+04 &  \\ 
       15:55:00 & 1.8076986667e+04 &  \\ 
       16:00:00 & 1.8082966667e+04 &  \\ 
       16:05:00 & 1.7903206667e+04 &  \\ 
       16:10:00 & 1.8063913333e+04 &  \\ 
       16:15:00 & 1.8355030000e+04 &  \\ 
       16:20:00 & 1.7971580000e+04 &  \\ 
       16:25:00 & 1.7797153333e+04 &  \\ 
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

>>>>

\subsection{Run configuration}
\label{subsec:3.2}
The COSMO-ART model uses NAMELIST-input to specify runtime parameters
splitted into several groups (see Table~\ref{tab:1}).

\begin{table}[htbf]
  \begin{center}
    \caption{}
    \label{tab:1}
    \begin{tabular}{ll}
      \hline\noalign{\smallskip} 
      \textbf{Group} & \textbf{Description} \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      LMGRID & Grid domain and size parameters \\
      RUNCTL & Model run parameters \\
      TUNING & Physics and dynamics parameters \\
      DYNCTL & Adiabatic model parameters \\
      PHYCTL & Diabatic model parameters \\
      COSMO\_ART & Gases and aerosols model parameters \\
      DIACTL & Diagnostic calculations parameters \\
      SATCTL & Synthetic satellite images parameters \\
      IOCTL & I/O environment parameters \\
      GRIBIN & GRIB input parameters \\
      GRIBOUT & GRIB output parameters \\
     \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

@@

\subsubsection{Monch (CSCS - ETH Zurich)}
\begin{figure}[htbf]
  \includegraphics[width=0.4\textwidth]{Figs/NRJ_benchmark_Monch.eps}
  \caption{Isola E1 Rack 2 Total Power and Isola E1 Total Power}
  \label{fig:1}
\end{figure}

@@

The power  consumption for  both jobs is  calculated by  averaging the
corresponding power  measurements from the Excel  file.  Power results
account for the  Isola E1 Rack 2 Total Power. As  time resolution is 5
minutes  for the  output  results, the  average  power consumption  is
computed   by  considering  6   values  for   each  single   run  (see
Table~\ref{tab:2}).

\begin{table}
  \begin{center}
    \caption{}
    \label{tab:2}
    \begin{tabular}{lll}
      \hline\noalign{\smallskip}
      \textbf{Time} & \textbf{Measured power (W)} & \textbf{Average power (W)} \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      12:55:00 & 1.2355833333e+04 & 1.265852278e+04 \\ 
      13:00:00 & 1.2820266667e+04 &  \\
      13:05:00 & 1.2600743333e+04 &  \\ 
      13:10:00 & 1.2811580000e+04 &  \\
      13:15:00 & 1.2609680000e+04 &  \\
      13:20:00 & 1.2753033333e+04 &  \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
      14:30:00 & 1.2019266667e+04 & 1.258640833e+04 \\ 
      14:35:00 & 1.2632253333e+04 &  \\
      14:40:00 & 1.2779040000e+04 &  \\
      14:45:00 & 1.2753180000e+04 &  \\
      14:50:00 & 1.2610476667e+04 &  \\
      14:55:00 & 1.2724233333e+04 &  \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

@@

\subsubsection{Pilatus (CSCS - ETH Zurich)}
\begin{figure}[htbf]
  \includegraphics[width=0.4\textwidth]{Figs/NRJ_benchmark_Pilatus.eps}
  \caption{Isola HD Pilatus Total Power}
  \label{fig:2}
\end{figure}

@@

Again, the power  consumption for all jobs is  calculated by averaging
the  corresponding  power  measurements  from the  Excel  file.  Power
results  account  for  the  Isola  HD Pilatus  Total  Power.  As  time
resolution  is 5  minutes for  the output  results, the  average power
consumption is computed by considering  4 values for each single 1-day
run and 9 values for the 2-days run (see Table~\ref{tab:3}).

\begin{table}
  \begin{center}
    \caption{}
    \label{tab:3}
    \begin{tabular}{lll}
      \hline\noalign{\smallskip}
      \textbf{Time} & \textbf{Measured power (W)} & \textbf{Average power (W)}  \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
       13:10:00 & 1.7824080000e+04 & 1.812201417e+04 \\ 
       13:15:00 & 1.8293650000e+04 &  \\ 
       13:20:00 & 1.8125140000e+04 &  \\ 
       13:25:00 & 1.8245186667e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       13:50:00 & 1.7849206667e+04 & 1.797961083e+04 \\ 
       13:55:00 & 1.7977790000e+04 &  \\ 
       14:00:00 & 1.8030646667e+04 &  \\ 
       14:05:00 & 1.8060800000e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       14:30:00 & 1.7868826667e+04 & 1.806545167e+04 \\ 
       14:35:00 & 1.8115786667e+04 &  \\ 
       14:40:00 & 1.8188520000e+04 &  \\ 
       14:45:00 & 1.8088673333e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       15:15:00 & 1.7857800000e+04 & 1.797302833e+04 \\ 
       15:20:00 & 1.7962513333e+04 &  \\ 
       15:25:00 & 1.8078226667e+04 &  \\ 
       15:30:00 & 1.7993573333e+04 &  \\ 
      \noalign{\smallskip}\hline\noalign{\smallskip}
       15:45:00 & 1.7801980000e+04 & 1.799757815e+04 \\ 
       15:50:00 & 1.7925386667e+04 &  \\ 
       15:55:00 & 1.8076986667e+04 &  \\ 
       16:00:00 & 1.8082966667e+04 &  \\ 
       16:05:00 & 1.7903206667e+04 &  \\ 
       16:10:00 & 1.8063913333e+04 &  \\ 
       16:15:00 & 1.8355030000e+04 &  \\ 
       16:20:00 & 1.7971580000e+04 &  \\ 
       16:25:00 & 1.7797153333e+04 &  \\ 
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}
